### 2020-06-05 report/sections/server/react.tex
Report: complete chapter 5 approach

\section{Summary}
\begin{itemize}
\item static guarantees on avoiding communication mismatch
\item static guarantees on affine channel usage
\item leverage the react framework to express the model types approach from Fowler 2020 appropriately, to provide static guarantees, by construction, that the channel actions made available at each state respect the protocol, and by definition, multiparty session type safety
\end{itemize}

>>>>

%\section{Summary}
%\begin{itemize}
%\item static guarantees on avoiding communication mismatch
%\item static guarantees on affine channel usage
%\item leverage the react framework to express the model types approach from Fowler 2020 appropriately, to provide static guarantees, by construction, that the channel actions made available at each state respect the protocol, and by definition, multiparty session type safety
%\end{itemize}

### 2020-06-05 report/sections/server/react/approach.tex
Report: complete chapter 5 approach

We leverage the correspondence between model types and states in the EFSM:
each state in the EFSM is a model type, the set of messages represent
the possible (IO) actions available at that state,
and the update function defines which successor state to transition to,
given the supported IO actions at this state.

\subsection{The React Framework}
We implement model types for the EFSM on top of the 
\emph{React.js} framework developed by Facebook \cite{React}.
React is widely used in industry to create scalable single-page
TypeScript applications, so this makes our workflow beneficial in an
industrial context. 
The framework defines a way for data to flow
between UI elements, and empowers the UI to subscribe and
``react'' to data changes.
We aim to implement similar behaviour with respect to the EFSM:
the UI should react to EFSM state transitions,
so we can ensure -- preferably statically -- that the
channel actions ``present'' on the browser at any given time
are those permitted by the current EFSM state.

@@

\paragraph{Components}
A \textit{component} is a reusable UI element which
contains its own mark-up and logic.
Components implement a \texttt{render()} method which returns
a React element, the smallest building blocks of a React application.
This is analogue to the \textit{view} function in the MVU architecture.
React uses the \textit{JSX} syntax extension \cite{JSX}
to interpolate TypeScript logic 
(enclosed in curly braces)
within HTML mark-up: 
in \cref{line:childrender}, the \texttt{Count} component
evaluates the TypeScript expression 
\lstonelinejs{this.props.count} and renders it in bold on the web page.
Components can render other components, which give rise to
a tree of UI elements. \cref{line:parentrender} shows that our
\texttt{Count} component is rendered by 
another component, \texttt{App}.

>>>>

We leverage the correspondence between model types and states in the EFSM:
each state in the EFSM is a model type, the set of messages represent
the possible channel actions available at that state,
and the update function defines which successor state to transition to,
given the supported channel actions at this state.

We implement model types for the EFSM on top of the 
\emph{React.js} framework developed by Facebook \cite{React}.
React is widely used in industry to create scalable single-page
TypeScript applications, so this makes our workflow beneficial in an
industrial context. 
The framework defines a way for data to flow
between UI elements, and empowers the UI to subscribe and
``react'' to data changes.
We aim to implement similar behaviour with respect to the EFSM:
the UI should react to EFSM state transitions,
so we can \textbf{statically} ensure that the
channel actions ``present'' on the browser at any given time
are those permitted by the current EFSM state.
We introduce the framework in \cref{subsection:react}.

When executing \fancyname{SessionTS} to generate code
for the \trole{Client} endpoint specifying the
\texttt{browser} target, the developer obtains the following 
groups of files:

\begin{itemize}

\item 
\textbf{S[40-43].tsx:}
Developer APIs for implementing EFSM states 
(\cref{section:reactefsm});

\begin{itemize}
\item
\textbf{EFSM.ts}, \textbf{Message.ts}, \textbf{Roles.ts:}
Utility types for EFSM encoding;
\end{itemize}

\item 
\textbf{Client.tsx:} 
Session runtime for executing the EFSM 
(\cref{section:reactruntime});

\begin{itemize}
\item
\textbf{Session.ts}, \textbf{Types.ts:}
Utility types for session runtime.
\end{itemize}

\end{itemize}

\subsection{The React Framework}
\label{subsection:react}

@@

\paragraph{Components}
A \textit{component} is a reusable UI element which
contains its own mark-up and logic.
Components implement a \texttt{render()} method which returns
a React element, the smallest building blocks of a React application.
This is analogue to the \textit{view} function in the MVU architecture.
React uses the \textit{JSX} syntax extension \cite{JSX}
to interpolate TypeScript logic 
(enclosed in curly braces)
within HTML mark-up: 
in \cref{line:childrender}, the \texttt{Count} component
evaluates the TypeScript expression 
\lstonelinejs{this.props.count} and renders it in bold on the web page.

Components can render other components, which give rise to
a tree of UI elements. \cref{line:parentrender} shows that our
\texttt{Count} component is rendered by 
the \texttt{App} component.
